### 2020-02-06 README.Rmd
small change to filter out resprouts
specify of growth

```{r}
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% filter(codes != 'R')
id <- "treeID"

@@

```{r, cache = TRUE}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh") +
  coord_cartesian(xlim = c(-0.5, 1))
```

>>>>

```{r}
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% filter(!str_detect(codes,'R'))
id <- "treeID"

@@

```{r, cache = TRUE}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```
